[Re] Non-additive coupling enables propagation of synchronous spiking activity in purely random networks

### 2018-03-13 article/Caze_2018.tex
correcting last supp figure again

\begin{figure}[h]
\centering
\begin{subfigure}[t]{0.5\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/markov_l_dt_100us.pdf}
\end{subfigure}%
\begin{subfigure}[t]{0.5\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/markov_nl_dt_100us.pdf}
\end{subfigure}
\caption{\label{fig:markov}
\textbf{Evolution of synchronous pulses without correction in linearly (A) and non-linearly (B) coupled networks, corrected for the background activity.} All conventions as in Fig.~\ref{fig:markov_corrected}. The numerical results shown here (gray lines and green squares) are not corrected for the bias introduced by the clock-driven integration method (see text for details).}
\end{figure}
\end{document}

>>>>

\begin{figure}[h]
\centering
\begin{subfigure}[t]{0.5\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/markov_l_dt_100us.pdf}
\end{subfigure}%
\begin{subfigure}[t]{0.5\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/markov_nl_dt_100us.pdf}
\end{subfigure}
\caption{\label{fig:markov}
\textbf{Evolution of synchronous pulses without correction in linearly (A) and non-linearly (B) coupled networks.} All conventions as in Fig.~\ref{fig:markov_corrected}. The numerical results shown here (gray lines and green squares) are not corrected for the bias introduced by the clock-driven integration method (see text for details).}
\end{figure}
\end{document}
